% src/03_analytical-work/default.tex

\section{Analytical work}
	Now that the fundamental principles have been established, this chapter focuses on addressing the key questions outlined in Chapter~\ref{sec:scope-objectives}.
	First, the geometry of the assembly is defined more rigorously to enable the determination of characteristic lengths and cross-sectional areas at all relevant locations.
	Additionally, the conditions within the reservoir and the vacuum environment are specified, as they significantly influence the resulting flow behavior.

	Subsequently, the expected flow regimes are discussed to verify whether the isentropic continuum flow model introduced earlier is applicable.
	These assumptions will then be validated through analytical calculations.
	As a starting point, the assembly is approximated as a variable-area duct without leakage, allowing the application of one-dimensional isentropic flow formulations and a direct assessment of the assumptions made in the preceding chapter.

	This simplification, however, comes at a cost—primarily by neglecting the detailed geometry of the reactor and potential non-isentropic effects.
	Therefore, a dedicated section will briefly address flow behavior in micro-channels, particularly the problem of slip at the boundaries.
	This lays the groundwork for a refined approach in which the reactor is treated as a separate reservoir with its own stagnation conditions.

	Recognizing that variations in stagnation conditions inherently correspond to non-isentropic flow behavior, this framework attempts to capture such effects while still applying isentropic analysis to isolated components of the system.
	This also enables the inclusion of mass flow through leaks in the reactor, whose influence on the Mach number at the inlet throat will be investigated.

	Finally, it will be argued why the presented formulations are insufficient to accurately resolve the velocity distribution at the outlet.
	As a result, possible numerical approaches for addressing this limitation will be discussed.

\subsection{Geometry and flow characteristics of the components}\label{sec:geometry}
	\input{src/03_analytical-work/geometry-of-the-components.tex}

\subsection{Expected flow regimes}\label{sec:expected-flow-regimes}
	\input{src/03_analytical-work/expected_flow_regimes.tex}
	\newpage

\subsection{One-dimensional isentropic variable area flow}\label{sec:one-dim-isentropic}
	\input{src/03_analytical-work/full_1-d_isentropic.tex}
	\newpage

\subsection{Flow behaviors in micro-channels}\label{sec:micro-channels}
	\input{src/03_analytical-work/micro_channels.tex}
	\newpage

\subsection{Including non-isentropic behaviors}\label{sec:disconnected-reservoirs}
	\input{src/03_analytical-work/reactor_reservoir_leak.tex}
	\newpage

\subsection{Under-expanded nozzle plume at outlet}\label{sec:outlet_plume}
	\input{src/03_analytical-work/under_expanded_plume_outlet.tex}
	\newpage
